---
title: "PLOS Medicine Revisions - Model Diagnostics"
author: "Matt Hickey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
always_allow_html: true
---



```{r setup, include=FALSE}

library(tidyverse)
library(RColorBrewer)
library(ggrepel)

options(tinytex.verbose = TRUE)
options(scipen = 999)


knitr::opts_chunk$set(echo = FALSE, fig.height=10, fig.width=15)
knitr::opts_knit$set(root.dir = '~/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration')

pct <- function(x) {
  y <- paste0(round((x*100),0),"%")
  return(y)
}

load("~/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration/SynthesisHTN_105.RData")

df_netdaly_distribution <- df_netdaly_distribution %>% 
  rename(policy = source)
df_netdaly <- df_netdaly %>% 
  rename(policy = source)


```

# Net DALYs averted across different cost-effectiveness thresholds
```{r}

df_netdaly_distribution %>% mutate(ce_threshold = as.numeric(ce_threshold)) %>% 
  filter(year == "2474", cost_cat == "Base case cost assumptions", ce_threshold >50) %>% 
  group_by(policy, ce_threshold) %>% 
  summarize(netdaly = median(netdaly_averted),
            quantile_05 = quantile(netdaly_averted, 0.05),
            quantile_95 = quantile(netdaly_averted, 0.95)) %>% 
  ggplot(aes(x = ce_threshold, fill = policy, color=policy)) +
  geom_line(aes(y = netdaly)) +
  geom_ribbon(aes(ymin = quantile_05, ymax = quantile_95), color = NA, show.legend = FALSE, alpha = 0.1) + 
  coord_cartesian(xlim = c(0,1000)) +
  theme_classic(base_size = 16) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10), limits = c(0,1000)) + 
  labs(title = "B. Net DALYs averted by cost-effectiveness threshold",
       subtitle = "Median (90% range), estimated for population of 10 million adults over 50-year time horizon from 2024-2074",
       y = "Net DALYs averted (thousands)",
       x = "Cost-effectiveness threshold (USD/DALY averted)") +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "#636363"),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_fill_brewer(palette = "Dark2")


```

# Net DALYs averted probability distribution
At CE threshold $500 USD/DALY averted
```{r}
# Get the Brewer palette colors
colors <- RColorBrewer::brewer.pal(n = 3, name = "Dark2")  # Adjust n as needed
colors <- colors[-1]  # Remove the first color

df_netdaly %>% 
  filter(year == "2474", cost_cat == "Base case cost assumptions", policy != "SOC") %>% 
  ggplot(aes(x = netdaly_averted, fill = policy, color = policy)) +
  geom_density(alpha = 0.5) +  # Standard density plot with transparency
  geom_rug(alpha = 0.5, sides = "b") +  # Add rug plot
  theme_classic(base_size = 16) +
  labs(
    title = "Net DALYs averted at CE threshold of $500 USD/DALY averted",
    subtitle = "Median (90% range), estimated for population of 10 million adults over 50-year time horizon from 2024-2074",
    x = "Net DALYs averted (thousands)",
    y = "Density"
  ) +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "#636363"),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_manual(values = colors) +  # Use the modified color vector
  scale_fill_manual(values = colors)    # Use the modified color vector

```


# Cost-effectiveness frontiers with scatterplot
Including all data points to show distribution around ICER estimates
```{r}
# Extract ICER values for annotations
plot_icer_base <- plot_icer %>% 
  rename(policy = source) %>% 
  filter(cost_cat == "Base case cost assumptions") %>% 
  mutate(icer_text = ifelse(is.na(icer2), NA, paste0("$", icer2, "/DALY")),
         nudge_y = ifelse(policy == "CCC", 6, 
                          ifelse(policy == "CHW", 0, NA)))
  
ccc_icer <- plot_icer_base %>% filter(policy == "CCC") %>% ungroup() %>% select(icer2)
chw_icer <- plot_icer_base %>% filter(policy == "CHW") %>% ungroup() %>% select(icer2)

# Create the overlayed plot
combined_plot <- ggplot() +
  # Axis lines at x=0 and y=0
  geom_hline(yintercept = 0, color = "#636363", linetype = "solid") +
  geom_vline(xintercept = 0, color = "#636363", linetype = "solid") +
  # First plot: Points from df_netdaly
  geom_point(data = df_netdaly %>% filter(year == "2474", cost_cat == "Base case cost assumptions", policy != "SOC"),
             aes(x = ddaly_averted, y = cost_inc, color = policy), alpha = 0.4) +
  # Second plot: Lines and points from plot_icer_base
  geom_line(data = plot_icer_base %>% filter(cost_cat == "Base case cost assumptions"),
            aes(x = mean_ddaly, y = mean_cost),
            linewidth = 1.5) +
  geom_point(data = plot_icer_base %>% filter(cost_cat == "Base case cost assumptions"),
             aes(x = mean_ddaly, y = mean_cost)) +
  # ggrepel annotations
  geom_label_repel(aes(label = ifelse(is.na(icer_text), NA, icer_text)), 
                   nudge_y = plot_icer_base$nudge_y,
                   nudge_x = -10,
                   direction = "y",  # Keep labels in a vertical column
                   hjust = 0,  # Left-align the text
                   segment.size = 0.2,
                   force = 1,
                   min.segment.length = 0,
                   show.legend = FALSE) +
  # Lines from points to annotations
  geom_segment(data = plot_icer_base %>% filter(policy == "SOC"),
               aes(x = mean_ddaly, y = mean_cost, xend = -20, yend = 6),
               color = "lightgray") +
  geom_segment(data = plot_icer_base %>% filter(policy == "CCC"),
               aes(x = mean_ddaly, y = mean_cost, xend = 158, yend = 6),
               color = "lightgray") +
  geom_segment(data = plot_icer_base %>% filter(policy == "CHW"),
               aes(x = mean_ddaly, y = mean_cost, xend = 165, yend = 22),
               color = "lightgray") +
  # Shared labels, theme, and scales
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  labs(title = "Cost-effectiveness frontier",
       subtitle = "Per 10 million adults over 50-year time horizon (2024 - 2074), n=3000 setting-scenarios",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  # Annotations
  annotate("text", x=-32, y=6, label= "SOC", size = 8) +
  annotate("text", x=200, y=6, label= "Chronic Care Clinic", size = 8) +
  annotate("text", x=200, y=4, label= paste0("$",ccc_icer, "/DALY"), size = 8, font = "bold") +
  annotate("text", x=200, y=22, label= "CHW Screening", size = 8) +
  annotate("text", x=200, y=20, label= paste0("$",chw_icer, "/DALY"), size = 8) +
  theme_classic(base_size = 16) +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "#636363"),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_manual(values = colors) +  # Use the modified color vector
  scale_fill_manual(values = colors)    # Use the modified color vector

# Display the combined plot
print(combined_plot)
```

Including selected paired datapoints (for illustration only)
```{r}
# # Extract ICER values for annotations
# 
# # Create the overlayed plot
# combined_plot <- ggplot() +
#   # First plot: Points from df_netdaly
#   geom_point(data = df_netdaly %>% filter(year == "2474", cost_cat == "Base case cost assumptions"),
#              aes(x = ddaly_averted, y = cost_inc, color = policy), alpha = 0.4) +
#   # Lines grouped by country with light grey and removed from legend
#   geom_line(
#     data = df_netdaly %>% filter(year == "2474", cost_cat == "Base case cost assumptions", policy != "SOC", country < 12000000) %>% mutate(country = as.character(country)),
#     aes(x = ddaly_averted, y = cost_inc, group = country),  # Group by country
#     color = "#636363",  # Set color to light grey
#     show.legend = FALSE   # Remove from legend
#   ) +
#   # Second plot: Lines and points from plot_icer
#   geom_line(data = plot_icer %>% filter(cost_cat == "Base case cost assumptions"),
#             aes(x = mean_ddaly, y = mean_cost),
#             linewidth = 1.5) +
#   geom_point(data = plot_icer %>% filter(cost_cat == "Base case cost assumptions"),
#              aes(x = mean_ddaly, y = mean_cost)) +
#   # Shared labels, theme, and scales
#   scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) + 
#   scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
#   labs(title = "Cost-effectiveness frontier",
#        subtitle = "Per 10 million adults over 50-year time horizon (2024 - 2074), n=3000 setting-scenarios",
#        y = "Annual incremental cost (millions $USD)",
#        x = "Annual DALYs averted (thousands)") +
#   theme_classic(base_size = 16) +
#   theme(
#     plot.title = element_text(size = 20, face = "bold", color = "#636363"),
#     legend.position = "bottom",
#     text = element_text(color = "#636363"),
#     axis.line = element_line(color = "#636363"),
#     axis.ticks = element_line(color = "#636363"),
#     axis.text = element_text(color = "#636363")
#   ) +
#   scale_color_brewer(palette = "Dark2")
# 
# # Display the combined plot
# print(combined_plot)
```


# Hypertension diagnosis, treatment, control over time
## Age 18+
### 0.25-Year Increments
```{r}
load("~/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration/run105_long.RData")

sourcenames <- c("SOC", "CCC", "CHW")
df$policy <- factor(df$policy, levels = sourcenames)
df_yr$policy <- factor(df_yr$policy, levels = sourcenames)

# List of variables and their y-axis labels
variables_ge18 <- list(
  p_htn_ge18 = "Prevalence of hypertension among adults aged 18+ years",
  p_diag_htn_ge18 = "Proportion of adults aged 18+ years with hypertension who are diagnosed",
  p_on_tx_htn_ge18 = "Proportion of adults aged 18+ years with hypertension who are treated",
  p_htn_ctrl_ge18 = "Proportion of adults aged 18+ years with hypertension with SBP <140"
)

# List of plot titles
plot_titles_ge18 <- list(
  p_htn_ge18 = "Hypertension Prevalence",
  p_diag_htn_ge18 = "Hypertension Diagnosis",
  p_on_tx_htn_ge18 = "Hypertension Current Treatment",
  p_htn_ctrl_ge18 = "Hypertension Control"
)

# Loop over variables to create summary data and plots
plots_ge18 <- list()

for (var in names(variables_ge18)) {
  # Summarize data
  summary_df <- df %>%
    group_by(cald, policy) %>%
    summarize(
      median = median(.data[[var]]),
      lower_90 = quantile(.data[[var]], 0.05),
      upper_90 = quantile(.data[[var]], 0.95),
      .groups = "drop"
    )
  
  # Generate plot
  p <- ggplot(summary_df, aes(x = cald, color = policy, fill = policy)) +
    geom_line(aes(y = median), size = 1.2) +  # Median line
    geom_ribbon(aes(ymin = lower_90, ymax = upper_90), alpha = 0.2) +  # Shaded 90% range
    labs(
      title = plot_titles_ge18[[var]],
      x = "Time (3-month intervals)",
      y = variables_ge18[[var]],  # Custom y-axis label
      color = "Policy",
      fill = "Policy"
    ) +
    theme_minimal()  +
    scale_y_continuous(limits = c(0, NA)) +
    theme(
      plot.title = element_text(size = 18, face = "bold"),  # Increase plot title size
      axis.title.x = element_text(size = 14),              # Increase x-axis title size
      axis.title.y = element_text(size = 14),              # Increase y-axis title size
      axis.text = element_text(size = 12),                 # Increase axis tick labels size
      legend.title = element_text(size = 14),              # Increase legend title size
      legend.text = element_text(size = 12)                # Increase legend text size
    ) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")
  
  # Add to list of plots
  plots_ge18[[var]] <- p
}

# Display plots
print(plots_ge18[["p_htn_ge18"]])
print(plots_ge18[["p_diag_htn_ge18"]])
print(plots_ge18[["p_on_tx_htn_ge18"]])
print(plots_ge18[["p_htn_ctrl_ge18"]])
```

### 1 year increments
```{r}
# plots_ge18_yr <- list()
# 
# # Create plots for data frame compressed one row per year
# for (var in names(variables_ge18)) {
#   # Summarize data
#   summary_df_yr <- df_yr %>%
#     group_by(year, policy) %>%
#     summarize(
#       median = median(.data[[var]]),
#       lower_90 = quantile(.data[[var]], 0.05),
#       upper_90 = quantile(.data[[var]], 0.95),
#       .groups = "drop"
#     )
#   
#   # Generate plot
#   p2 <- ggplot(summary_df_yr, aes(x = year, color = policy, fill = policy)) +
#     geom_line(aes(y = median), size = 1.2) +  # Median line
#     geom_ribbon(aes(ymin = lower_90, ymax = upper_90), alpha = 0.2) +  # Shaded 90% range
#     labs(
#       title = plot_titles_ge18[[var]],
#       x = "Year",
#       y = variables_ge18[[var]],  # Custom y-axis label
#       color = "Policy",
#       fill = "Policy"
#     ) +
#     theme_minimal() +
#     theme(
#       plot.title = element_text(size = 18, face = "bold"),  # Increase plot title size
#       axis.title.x = element_text(size = 14),              # Increase x-axis title size
#       axis.title.y = element_text(size = 14),              # Increase y-axis title size
#       axis.text = element_text(size = 12),                 # Increase axis tick labels size
#       legend.title = element_text(size = 14),              # Increase legend title size
#       legend.text = element_text(size = 12)                # Increase legend text size
#     )
#   
#   # Add to list of plots
#   plots_ge18_yr[[var]] <- p2
# }
# 
# # Display plots
# print(plots_ge18_yr[["p_htn_ge18"]])
# print(plots_ge18_yr[["p_diag_htn_ge18"]])
# print(plots_ge18_yr[["p_on_tx_htn_ge18"]])
# print(plots_ge18_yr[["p_htn_ctrl_ge18"]])
# ```
# 
# 
# ## Age 45-64
# ### 0.25 year increments
# ```{r}
# # List of variables and their y-axis labels
# variables_4564 <- list(
#   p_htn_4564 = "Prevalence of hypertension among adults aged 45-64 years",
#   p_diag_htn_4564 = "Proportion of adults aged 45-64 years with hypertension who are diagnosed",
#   p_on_tx_htn_4564 = "Proportion of adults aged 45-64 years with hypertension who are treated",
#   p_htn_ctrl_4564 = "Proportion of adults aged 45-64 years with hypertension with SBP <140"
# )
# 
# # List of plot titles
# plot_titles_4564 <- list(
#   p_htn_4564 = "Hypertension Prevalence",
#   p_diag_htn_4564 = "Hypertension Diagnosis",
#   p_on_tx_htn_4564 = "Hypertension Current Treatment",
#   p_htn_ctrl_4564 = "Hypertension Control"
# )
# 
# # Loop over variables to create summary data and plots
# plots <- list()
# 
# for (var in names(variables_4564)) {
#   # Summarize data
#   summary_df <- df %>%
#     group_by(cald, policy) %>%
#     summarize(
#       median = median(.data[[var]]),
#       lower_90 = quantile(.data[[var]], 0.05),
#       upper_90 = quantile(.data[[var]], 0.95),
#       .groups = "drop"
#     )
#   
#   # Generate plot
#   p <- ggplot(summary_df, aes(x = cald, color = policy, fill = policy)) +
#     geom_line(aes(y = median), size = 1.2) +  # Median line
#     geom_ribbon(aes(ymin = lower_90, ymax = upper_90), alpha = 0.2) +  # Shaded 90% range
#     labs(
#       title = plot_titles_4564[[var]],
#       x = "time (3-month intervals)",
#       y = variables_4564[[var]],  # Custom y-axis label
#       color = "Policy",
#       fill = "Policy"
#     ) +
#     theme_minimal() +
#     theme(
#       plot.title = element_text(size = 18, face = "bold"),  # Increase plot title size
#       axis.title.x = element_text(size = 14),              # Increase x-axis title size
#       axis.title.y = element_text(size = 14),              # Increase y-axis title size
#       axis.text = element_text(size = 12),                 # Increase axis tick labels size
#       legend.title = element_text(size = 14),              # Increase legend title size
#       legend.text = element_text(size = 12)                # Increase legend text size
#     )
#   
#   # Add to list of plots
#   plots[[var]] <- p
# }
# 
# # Display plots
# print(plots[["p_htn_4564"]])
# print(plots[["p_diag_htn_4564"]])
# print(plots[["p_on_tx_htn_4564"]])
# print(plots[["p_htn_ctrl_4564"]])
# 
# ```
# 
# 
# ### 1 year increments
# ```{r}
# plots2 <- list()
# # create plots for data frame compressed one row per year
# for (var in names(variables_4564)) {
#   # Summarize data
#   summary_df_yr <- df_yr %>%
#     group_by(year, policy) %>%
#     summarize(
#       median = median(.data[[var]]),
#       lower_90 = quantile(.data[[var]], 0.05),
#       upper_90 = quantile(.data[[var]], 0.95),
#       .groups = "drop"
#     )
#   
#   # Generate plot
#   p2 <- ggplot(summary_df_yr, aes(x = year, color = policy, fill = policy)) +
#     geom_line(aes(y = median), size = 1.2) +  # Median line
#     geom_ribbon(aes(ymin = lower_90, ymax = upper_90), alpha = 0.2) +  # Shaded 90% range
#     labs(
#       title = plot_titles_4564[[var]],
#       x = "Year",
#       y = variables_4564[[var]],  # Custom y-axis label
#       color = "Policy",
#       fill = "Policy"
#     ) +
#     theme_minimal() +
#     theme(
#       plot.title = element_text(size = 18, face = "bold"),  # Increase plot title size
#       axis.title.x = element_text(size = 14),              # Increase x-axis title size
#       axis.title.y = element_text(size = 14),              # Increase y-axis title size
#       axis.text = element_text(size = 12),                 # Increase axis tick labels size
#       legend.title = element_text(size = 14),              # Increase legend title size
#       legend.text = element_text(size = 12)                # Increase legend text size
#     )
#   
#   # Add to list of plots
#   plots2[[var]] <- p2
# }
# 
# # Display plots
# print(plots2[["p_htn_4564"]])
# print(plots2[["p_diag_htn_4564"]])
# print(plots2[["p_on_tx_htn_4564"]])
# print(plots2[["p_htn_ctrl_4564"]])
```

