---
title: "Results"
author: "Matt Hickey"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(scales)
library(RColorBrewer)

options(tinytex.verbose = TRUE)
options(scipen = 999)

knitr::opts_chunk$set(echo = FALSE, message = F, fig.height=8, fig.width=12)
require("knitr")
opts_knit$set(root.dir = "/Users/sf124046/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration")

load("/Users/sf124046/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration/SynthesisHTN_106.RData")

pct <- function(x) {
  y <- ifelse(x < 0.1, paste0(round((x * 100), 1), "%"), paste0(round((x * 100), 0), "%"))
  return(y)
}

fx_pctmean_range <- function(data) {
  mean_val <- round(mean(data, na.rm = TRUE) * 100, 1)
  lower_val <- round(quantile(data, q = 0.05, na.rm = TRUE) * 100, 1)
  upper_val <- round(quantile(data, q = 0.95, na.rm = TRUE) * 100, 1)
  result <- paste0(mean_val, "% (", lower_val, "% to ", upper_val, "%)")
  return(result)
}

fx_mean_range <- function(data, digits = 2) {
  mean_val <- round(mean(data, na.rm = TRUE), digits)
  lower_val <- round(quantile(data, 0.05, na.rm = TRUE), digits)
  upper_val <- round(quantile(data, 0.95, na.rm = TRUE), digits)
  result <- paste0(mean_val, " (", lower_val, " to ", upper_val, ")")
  return(result)
}

y <- c("2474")
z <- c("_s1_age50")

```
# Tables

## Table 3. 
Hypertension care cascade and cardiovascular disease outcomes of hypertension policy scenarios over 50 years (2024-2074); Mean (90% range)

``` {r table3}


t3vars_m0 <- c("m_sbp")
t3vars_pct <- c("p_htn_true", "p_hypert160", "p_dx_htn_true", "p_dx_htn_over", "p_on_tx_htn", "p_ever_tx_htn", "p_on_tx_htn_over", "p_hypert_control")
t3vars_m2 <- c("rate_ihd_modsev", "rate_ihd_modsev_htn", "rate_ihd_modsev_rr", "rate_ihd_modsev_htn_rr",
               "rate_cva_modsev", "rate_cva_modsev_htn", "rate_cva_modsev_rr", "rate_cva_modsev_htn_rr", 
               "rate_dead_cvd", "rate_dead_cvd_rr", "rate_dead_hivpos_cvd", "rate_dead_hivpos_cvd_rr",
               "rate_dead_ac", "rate_dead_ac_rr", "rate_dead_hivpos_ac", "rate_dead_hivpos_ac_rr")

t3vars <- c(t3vars_m0, t3vars_pct, t3vars_m2)
t3age <- c("18+", "25-44", "45-64", "65+")

x1 <- df_sas %>% filter(year == y, var %in% t3vars, age %in% t3age) %>% 
  group_by(var, age, source) %>%
  summarize(mean_val = mean(value, na.rm = T),
            q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
            q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
  ungroup() %>% filter(!is.na(mean_val)) %>% 
  mutate(mean_value = ifelse(var %in% t3vars_m0, paste0(round(mean_val,0), " (", round(q05,0), " to ", round(q95,0), ")"),
                      ifelse(var %in% t3vars_pct, paste0(pct(mean_val), " (", pct(q05), " to ", pct(q95), ")"), 
                      ifelse(var %in% t3vars_m2, paste0(round(mean_val,2), " (", round(q05,2), " to ", round(q95,2), ")"), NA)))) %>% 
  arrange(match(var, t3vars), match(age, t3age)) %>% 
  select(var, age, source, mean_value) %>% 
  pivot_wider(names_from = source, values_from = mean_value)


write_csv(x1, paste0("./results/","t3_", y, z, ".csv"))
x1 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

```

## Table 4. 
Cost and cost-effectiveness of hypertension policies per 10 million adults over 50 years (2024-2074); Mean (90% range)

``` {r table4}


t3vars_m1 <- c("ddaly_averted", "dhtn_cost_scr", "dhtn_cost_clin", "dhtn_cost_drug", "dhtn_cost_cvd", "dhtn_cost_total",
               "htn_cost_scr", "htn_cost_clin", "htn_cost_drug", "htn_cost_cvd", "htn_cost_total")

t3vars <- c(t3vars_m1)
t3age <- c("18+", "25-44", "45-64", "65+", "All")

x2 <- df_sas %>% filter(year == y, var %in% t3vars, age %in% t3age) %>% 
  group_by(var, age, source) %>%
  summarize(mean_val = mean(value, na.rm = T),
            q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
            q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
  ungroup() %>% filter(!is.na(mean_val)) %>% 
  mutate(mean_value = ifelse(var %in% t3vars_m1, paste0(round(mean_val,1), " (", round(q05,1), " to ", round(q95,1), ")"), NA)) %>% 
  arrange(match(var, t3vars), match(age, t3age)) %>% 
  select(var, age, source, mean_value) %>% 
  pivot_wider(names_from = source, values_from = mean_value)

x3 <- df_netdaly %>% filter(year == y, cost_cat == "Base case cost assumptions") %>% 
  group_by(source) %>%
  summarize(inc_cost = paste0(round(mean(cost_inc, na.rm = T),1), 
                                     " (", round(quantile(cost_inc, 0.05, q = 0.05, na.rm = T),1), " to ", 
                                     round(quantile(cost_inc, 0.95, q=0.95, na.rm = T),1), ")"),
            netdaly_averted = paste0(round(mean(netdaly_averted, na.rm = T),1), 
                                     " (", round(quantile(netdaly_averted, 0.05, q = 0.05, na.rm = T),1), " to ", 
                                     round(quantile(netdaly_averted, 0.95, q=0.95, na.rm = T),1), ")"),
            cf_any = pct(mean(cf_netdaly_any, na.rm = T)),
            cf_all = pct(mean(cf_netdaly_all, na.rm = T))) %>%  
  ungroup() %>% 
  select(source, inc_cost, netdaly_averted, cf_any, cf_all) %>% 
  mutate(age = "All") %>% 
  pivot_longer(cols = c(inc_cost, netdaly_averted, cf_any, cf_all), names_to = "var") %>% 
  pivot_wider(names_from = source, values_from = value)


x4 <- rbind(x2, x3)
write_csv(x4, paste0("./results/","t4_", y, z, ".csv"))
x4 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
x <- rbind(x1, x4)

```

``` {r table3b}

# t3vars_pct <- c("p_htn_true160", "p_hypert160", "p_dx_htn_true160", "p_on_tx_htn160", "p_ever_tx_htn160", "p_hypert_control160")
# 
# t3vars <- c(t3vars_pct)
# t3age <- c("18+", "25-44", "45-64", "65+")
# 
# sev1 <- df_sas %>% filter(year == y, age %in% t3age, var %in% t3vars) %>% 
#   group_by(var, age, source) %>%
#   summarize(mean_val = mean(value, na.rm = T),
#             q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
#             q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
#   ungroup() %>% filter(!is.na(mean_val)) %>% 
#   mutate(mean_value = ifelse(var %in% t3vars_pct, paste0(pct(mean_val), " (", pct(q05), " to ", pct(q95), ")"), NA)) %>% 
#   arrange(match(var, t3vars)) %>% 
#   select(var, age, source, mean_value) %>% 
#   pivot_wider(names_from = source, values_from = mean_value)
# 
# # write_csv(sev1, paste0("./results/","sevhtn_", y, ".csv"))
# sev1 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

```


```{r cost-effectiveness table prep}
df_netdaly %>% 
  select(m_sbp_4564_23, p_htn_true_4564_23, p_diagnosed_hypert_4564_23, p_on_tx_htn_4564_23, p_hypert_control_4564_23, rate_dead_cvd_4564_23, prevalence1549_23) %>% 
  summary()

df_netdaly_params <- df_netdaly %>% 
  filter(year == y) %>% 
  mutate(sbp_cat = factor(ifelse(m_sbp_4564_23 <132, "<132",
                          ifelse(m_sbp_4564_23 >=132 & m_sbp_4564_23 <136, "132 to <136", 
                          ifelse(m_sbp_4564_23 >=136 & m_sbp_4564_23 <140, "136 to <140", 
                          ifelse(m_sbp_4564_23 >=140 , ">=140", NA)))),
                          levels = c("<132", "132 to <136", "136 to <140", ">=140"),
                          labels = c("<132", "132 to <136", "136 to <140", ">=140")),
         hiv_cat = factor(ifelse(prevalence1549_23 <0.05, "<5%",
                          ifelse(prevalence1549_23 >=0.05 & prevalence1549_23 <0.10, "5 to <10%", 
                          ifelse(prevalence1549_23 >=0.10 & prevalence1549_23 <0.15, "10 to <15%", 
                          ifelse(prevalence1549_23 >=0.15 , ">=15%", NA)))),
                          levels = c("<5%", "5 to <10%", "10 to <15%", ">=15%"),
                          labels = c("<5%", "5 to <10%", "10 to <15%", ">=15%")),
         htn_cat = factor(ifelse(p_htn_true_4564_23 <0.35, "<35%",
                          ifelse(p_htn_true_4564_23 >=0.35 & p_htn_true_4564_23 <0.43, "35 to <43%", 
                          ifelse(p_htn_true_4564_23 >=0.43 & p_htn_true_4564_23 <0.50, "43 to <50%", 
                          ifelse(p_htn_true_4564_23 >=0.50 , ">=50%", NA)))),
                          levels = c("<35%", "35 to <43%", "43 to <50%", ">=50%"),
                          labels = c("<35%", "35 to <43%", "43 to <50%", ">=50%")),
         dx_cat = factor(ifelse(p_diagnosed_hypert_4564_23 <0.22, "<22%",
                         ifelse(p_diagnosed_hypert_4564_23 >=0.22 & p_diagnosed_hypert_4564_23 <0.28, "22 to <28%", 
                         ifelse(p_diagnosed_hypert_4564_23 >=0.28 & p_diagnosed_hypert_4564_23 <0.36, "28 to <36%", 
                         ifelse(p_diagnosed_hypert_4564_23 >=0.36 , ">=36%", NA)))),
                         levels = c("<22%", "22 to <28%", "28 to <36%", ">=36%"),
                         labels = c("<22%", "22 to <28%", "28 to <36%", ">=36%")),
         tx_cat = factor(ifelse(p_on_tx_htn_4564_23  <0.04, "<4%",
                         ifelse(p_on_tx_htn_4564_23 >=0.04 & p_on_tx_htn_4564_23 <0.06, "4 to <6%", 
                         ifelse(p_on_tx_htn_4564_23 >=0.06 & p_on_tx_htn_4564_23 <0.09, "6 to <9%", 
                         ifelse(p_on_tx_htn_4564_23 >=0.09 , ">=9%", NA)))),
                         levels = c("<4%", "4 to <6%", "6 to <9%", ">=9%"),
                         labels = c("<4%", "4 to <6%", "6 to <9%", ">=9%")),
         ctrl_cat = factor(ifelse(p_hypert_control_4564_23 <0.02, "<2%",
                           ifelse(p_hypert_control_4564_23 >=0.02 & p_hypert_control_4564_23 <0.04, "2 to <4%", 
                           ifelse(p_hypert_control_4564_23 >=0.04 & p_hypert_control_4564_23 <0.06, "4 to <6%", 
                           ifelse(p_hypert_control_4564_23 >=0.06 , ">=6%", NA)))),
                           levels = c("<2%", "2 to <4%", "4 to <6%", ">=6%"),
                           labels = c("<2%", "2 to <4%", "4 to <6%", ">=6%")),
         cvd_cat = factor(ifelse(rate_dead_cvd_4564_23 < 0.4, "<400 per 100,000",
                          ifelse(rate_dead_cvd_4564_23 >=0.4 & rate_dead_cvd_4564_23 <0.5, "400 to <500 per 100,000", 
                          ifelse(rate_dead_cvd_4564_23 >=0.5 & rate_dead_cvd_4564_23 <0.6, "500 to <600 per 100,000", 
                          ifelse(rate_dead_cvd_4564_23 >=0.6 , ">=600 per 100,000", NA)))),
                           levels = c("<400 per 100,000", "400 to <500 per 100,000", "500 to <600 per 100,000", ">=600 per 100,000"),
                           labels = c("<400 per 100,000", "400 to <500 per 100,000", "500 to <600 per 100,000", ">=600 per 100,000")),
         setting_cvd_tx = factor(setting_cvd_tx),
         setting_cvd_tx_eff = factor(setting_cvd_tx_eff),
         setting_prob_htn_link = factor(setting_prob_htn_link)) %>% 
  select(country, source, cost_cat, year, cf_netdaly_any, cf_netdaly_all, sbp_cat, htn_cat, dx_cat, tx_cat, ctrl_cat, cvd_cat, setting_sbp_cal, setting_cvd_tx, setting_cvd_tx_eff, setting_cost_lowqual_cvd, setting_prob_htn_link, hiv_cat)

df_netdaly_paramsbase <- df_netdaly_params %>% filter(cost_cat == "Base case cost assumptions") 


```

## Table 5
Proportion of setting-scenarios where each hypertension policy is the most cost-effective over next 50 years (2024-2074), assuming a cost-effectiveness threshold of $500 USD per DALY averted

```{r table5}


z1 <- df_netdaly_params %>% 
  group_by(source, cost_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Cost scenarios") %>% 
  rename(prop = cost_cat)

# remainder only for cost scenarios = htn total
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, hiv_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "HIV prevalence among age 15-49")  %>% 
  rename(prop = hiv_cat)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cost_lowqual_cvd) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Cost of ineffective emergency CVD care compared to effective care")  %>% 
  rename(prop = setting_cost_lowqual_cvd)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cvd_tx_eff) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Proportion of acute CVD events receiving effective emergency care")  %>% 
  rename(prop = setting_cvd_tx_eff)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cvd_tx) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Proportion of acute CVD events receiving emergency care")  %>% 
  rename(prop = setting_cvd_tx)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_sbp_cal) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "SBP rise per decade after 2015",
         setting_sbp_cal = paste0(setting_sbp_cal*40, " mmHg"))  %>% 
  rename(prop = setting_sbp_cal)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, cvd_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "CVD mortality rate among adults aged 45-64")  %>% 
  rename(prop = cvd_cat)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, ctrl_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension control among adults aged 45-64")  %>% 
  rename(prop = ctrl_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, tx_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension treatment among adults aged 45-64")  %>% 
  rename(prop = tx_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, dx_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension diagnosis among adults aged 45-64")  %>% 
  rename(prop = dx_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, htn_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all)))%>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension prevalence among adults aged 45-64") %>% 
  rename(prop = htn_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, sbp_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all)))%>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Mean SBP among adults aged 45-64") %>% 
  rename(prop = sbp_cat) %>% 
  rbind(z1)

z1 <- z1 %>% select(parameter, prop, n, SOC, CCC, CHW)
write_csv(z1, paste0("./results/","t5_", y, z, ".csv"))
z1  %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
```

# Figures

## Figure 1. Hypertension Cascade among adults aged ≥18 years

```{r}
f1 <- df_sas %>% 
  filter(year == y, age %in% c("18+", "45-64"), var %in% c("p_dx_htn_true", "p_on_tx_htn", "p_hypert_control")) %>% 
  mutate(var = factor(var, 
                      levels = c("p_dx_htn_true", "p_on_tx_htn", "p_hypert_control"),
                      labels = c("Diagnosis", "Treatment (current)", "Hypertension control"))) %>% 
  group_by(source, var, age) %>% 
  summarize(mean = mean(value), q05 = quantile(value, 0.05), q95 = quantile(value, 0.95)) %>% 
  mutate(lower = mean - q05,
         upper = q95 - mean)

f1 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

f1 %>% 
  ggplot(aes(y = mean, x = source, fill = source)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=q05, ymax=q95, x = source), width = 0.4, color = "#636363") +
    facet_wrap(~ age + var) +
    theme_classic(base_size = 16) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")

```


## Figure 2. Cost-effectiveness of hypertension treatment policies
```{r icer}

plot_icer

ccc_icer <- plot_icer %>% filter(source == "CCC", cost_cat == "Base case cost assumptions") %>% ungroup() %>%  select(icer2)
chw_icer <- plot_icer %>% filter(source == "CHW", cost_cat == "Base case cost assumptions") %>% ungroup() %>%  select(icer2)

plot_icer %>% 
  filter(cost_cat %in% c("Base case cost assumptions")) %>% 
  ggplot(aes(x = mean_ddaly, y = mean_cost)) +
  geom_line() +
  geom_point() +
  annotate("text", x=0, y=1, label= "SOC", size = 5) +
  annotate("text", x=15, y=3, label= "Chronic Care Clinic", size = 5) +
  annotate("text", x=15, y=2, label= paste0("$",ccc_icer, "/DALY"), size = 5) +
  annotate("text", x=55, y=17, label= "CHW Screening", size = 5) +
  annotate("text", x=55, y=16, label= paste0("$",chw_icer, "/DALY"), size = 5) +
  theme_classic(base_size = 16) +
  coord_cartesian(ylim = c(0,20), xlim = c(0,70)) +
  labs(subtitle = "2024 - 2074",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "#636363"),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_brewer(palette = "Dark2")
```

## Figure 3. Cost-effectiveness of hypertension policies at varying cost-effectiveness thresholds
```{r cf_all_graph}
df_netdaly_graph %>% filter(year == "2474", cost_cat == "Base case cost assumptions") %>% 
  group_by(source, ce_threshold) %>% 
  summarize(prop = mean(cf_netdaly_all)) %>% 
  ggplot(aes(x = ce_threshold, y = prop, color=source)) +
  geom_line() +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1000)) +
  theme_classic(base_size = 16) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = dollar, limits = c(0,1000)) + 
  labs(subtitle = "2024-2074",
       y = "Proportion of settings policy is the most cost-effective",
       x = "Cost-effectiveness threshold (USD/DALY averted)") +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "#636363"),
    legend.position = "none",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_brewer(palette = "Dark2") +
  annotate("text", x=980, y=0.87, label= "CHW", size = 5, color = "#7570B3") +
  annotate("text", x=980, y=0.12, label= "CCC", size = 5, color = "#D95F02") +
  annotate("text", x=980, y=0.03, label= "SOC", size = 5, color = "#1B9E77") +
  annotate("text", x=100, y=1, label = "Domestic threshold, \nMalawi (approximate)", size = 5, color = "#636363") +
  annotate("text", x=300, y=1, label = "HIV threshold \n(lower)", size = 5, color = "#636363") +
  annotate("text", x=500, y=1, label = "HIV threshold \n(upper)", size = 5, color = "#636363") + 
  geom_segment(aes(x=500, y=0, xend=500, yend=0.9), linewidth = 0.2, linetype = "dashed", color = "#636363") +
  geom_segment(aes(x=100, y=0, xend=100, yend=0.9), linewidth = 0.2, linetype = "dashed", color = "#636363") + 
  geom_segment(aes(x=300, y=0, xend=300, yend=0.9), linewidth = 0.2, linetype = "dashed", color = "#636363")
  

```

