---
title: "Results"
author: "Matt Hickey"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(scales)
library(RColorBrewer)
library(patchwork)
library(ggrepel)

options(tinytex.verbose = TRUE)
options(scipen = 999)

knitr::opts_chunk$set(echo = FALSE, message = F, fig.height=10, fig.width=15)
require("knitr")
opts_knit$set(root.dir = "/Users/sf124046/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration")

load("/Users/sf124046/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration/SynthesisHTN_105.RData")

pct <- function(x) {
  y <- ifelse(x < 0.1, paste0(round((x * 100), 1), "%"), paste0(round((x * 100), 0), "%"))
  return(y)
}

fx_pctmean_range <- function(data) {
  mean_val <- round(mean(data, na.rm = TRUE) * 100, 1)
  lower_val <- round(quantile(data, q = 0.05, na.rm = TRUE) * 100, 1)
  upper_val <- round(quantile(data, q = 0.95, na.rm = TRUE) * 100, 1)
  result <- paste0(mean_val, "% (", lower_val, "% to ", upper_val, "%)")
  return(result)
}

fx_mean_range <- function(data, digits = 2) {
  mean_val <- round(mean(data, na.rm = TRUE), digits)
  lower_val <- round(quantile(data, 0.05, na.rm = TRUE), digits)
  upper_val <- round(quantile(data, 0.95, na.rm = TRUE), digits)
  result <- paste0(mean_val, " (", lower_val, " to ", upper_val, ")")
  return(result)
}

y <- c("2474")

```
# Tables

## Table 1. 
Characteristics relating to hypertension in 3000 setting scenarios in 2015*

```{r table1}

t1_hiv <- df_sas %>% filter(year == "15", var == "prevalence") %>% group_by(age) %>% summarize(hiv_mean = paste0(pct(median(value)), " (", round(100*quantile(value, 0.05, q = 0.05),0), " to ", pct(quantile(value, 0.95, q=0.95)), ")"))

t1_htn <- df_htn %>% filter(year == "15", source == "SOC") %>% group_by(age) %>% summarize(htn_mean = paste0(pct(mean(htn)), " (", round(100*quantile(htn, 0.05, q = 0.05),0), " to ", pct(quantile(htn, 0.95, q=0.95)), ")"))

t1_dx <- df_dx %>% filter(year == "15", source == "SOC") %>% group_by(age) %>% summarize(dx_mean = paste0(pct(mean(dx)), " (", round(100*quantile(dx, 0.05, q = 0.05),0), " to ", pct(quantile(dx, 0.95, q=0.95)), ")"))

t1_tx <- df_tx_current %>% filter(year == "15", source == "SOC", age %in% c("18+", "25-44", "45-64", "65+")) %>% group_by(age) %>% summarize(tx_mean = paste0(pct(mean(tx)), " (", round(100*quantile(tx, 0.05, q = 0.05),0), " to ", pct(quantile(tx, 0.95, q=0.95)), ")"))

t1_ctrl <- df_ctrl %>% filter(year == "15", source == "SOC", age %in% c("18+", "25-44", "45-64", "65+")) %>% group_by(age) %>% summarize(control_mean = paste0(pct(mean(control)), " (", round(100*quantile(control, 0.05, q = 0.05),0), " to ", pct(quantile(control, 0.95, q=0.95)), ")"))

t1_ssahtn <- df_htn %>% filter(age != "15-24", country %in% c("Kenya", "Uganda", "BurkinaFaso", "Swaziland", "SouthAfrica", "Tanzania", "Togo")) %>% mutate(htn = pct(htn)) %>% arrange(age, country)

t1_ssadx <- df_dx %>% filter(age != "15-24", country %in% c("Kenya", "Uganda", "BurkinaFaso", "Swaziland", "SouthAfrica", "Tanzania", "Togo")) %>% mutate(dx = pct(dx)) %>% arrange(age, country)

t1_htn %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+")) %>% 
  kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
t1_dx %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+")) %>% 
  kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
t1_tx %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
t1_ctrl %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

t1_hiv %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

# t1_ssahtn %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
# t1_ssadx %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

```

## Table 3. 
Hypertension care cascade and cardiovascular disease outcomes of hypertension policy scenarios over 50 years (2024-2074); Mean (90% range)

``` {r table3}
t3age <- c("18+", "25-44", "45-64", "65+")

x_over <- df_sas %>% filter(year == y, var %in% c("m_sbp_max_over", "m_sbp_over"), age %in% t3age) %>% 
  group_by(var, age, source) %>%
  summarize(mean_val = mean(value, na.rm = T),
            q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
            q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
  ungroup() %>% filter(!is.na(mean_val)) %>% 
  mutate(mean_value = paste0(round(mean_val,0), " (", round(q05,0), " to ", round(q95,0), ")")) %>% 
  select(var, age, source, mean_value) %>% 
  pivot_wider(names_from = source, values_from = mean_value)

x_over %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)


t3vars_m0 <- c("m_sbp")
t3vars_pct <- c("p_htn_true", "p_hypert160", "p_dx_htn_true", "p_dx_htn_over", "p_on_tx_htn", "p_ever_tx_htn", "p_on_tx_htn_over", "p_hypert_control")
t3vars_m2 <- c("rate_ihd_modsev", "rate_ihd_modsev_htn", "rate_ihd_modsev_rr", "rate_ihd_modsev_htn_rr",
               "rate_cva_modsev", "rate_cva_modsev_htn", "rate_cva_modsev_rr", "rate_cva_modsev_htn_rr", 
               "rate_dead_cvd", "rate_dead_cvd_rr", 
               "rate_dead_hivpos_cvd", "rate_dead_hivpos_cvd_rr",
               "rate_dead_ac", "rate_dead_ac_rr", "rate_dead_hivpos_ac", "rate_dead_hivpos_ac_rr")

t3vars <- c(t3vars_m0, t3vars_pct, t3vars_m2)


x1 <- df_sas %>% filter(year == y, var %in% t3vars, age %in% t3age) %>% 
  group_by(var, age, source) %>%
  summarize(mean_val = mean(value, na.rm = T),
            q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
            q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
  ungroup() %>% filter(!is.na(mean_val)) %>% 
  mutate(mean_value = ifelse(var %in% t3vars_m0, paste0(round(mean_val,0), " (", round(q05,0), " to ", round(q95,0), ")"),
                      ifelse(var %in% t3vars_pct, paste0(pct(mean_val), " (", pct(q05), " to ", pct(q95), ")"), 
                      ifelse(var %in% t3vars_m2, paste0(round(mean_val,2), " (", round(q05,2), " to ", round(q95,2), ")"), NA)))) %>% 
  arrange(match(var, t3vars), match(age, t3age)) %>% 
  select(var, age, source, mean_value) %>% 
  pivot_wider(names_from = source, values_from = mean_value)


write_csv(x1, paste0("./results/","t3_", y, ".csv"))
x1 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

```

## Table 4. 
Cost and cost-effectiveness of hypertension policies per 10 million adults over 50 years (2024-2074); Mean (90% range)

``` {r table4}


t3vars_m1 <- c("ddaly_averted", "dhtn_cost_scr", "dhtn_cost_clin", "dhtn_cost_drug", "dhtn_cost_cvd", "dhtn_cost_total",
               "htn_cost_scr", "htn_cost_clin", "htn_cost_drug", "htn_cost_cvd", "htn_cost_total")

t3vars <- c(t3vars_m1)
t3age <- c("18+", "25-44", "45-64", "65+", "All")

x2 <- df_sas %>% filter(year == y, var %in% t3vars, age %in% t3age) %>% 
  group_by(var, age, source) %>%
  summarize(mean_val = mean(value, na.rm = T),
            q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
            q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
  ungroup() %>% filter(!is.na(mean_val)) %>% 
  mutate(mean_value = ifelse(var %in% t3vars_m1, paste0(round(mean_val,1), " (", round(q05,1), " to ", round(q95,1), ")"), NA)) %>% 
  arrange(match(var, t3vars), match(age, t3age)) %>% 
  select(var, age, source, mean_value) %>% 
  pivot_wider(names_from = source, values_from = mean_value)

x3 <- df_netdaly %>% filter(year == y, cost_cat == "Base case cost assumptions") %>% 
  group_by(source) %>%
  summarize(inc_cost = paste0(round(mean(cost_inc, na.rm = T),1), 
                                     " (", round(quantile(cost_inc, 0.05, q = 0.05, na.rm = T),1), " to ", 
                                     round(quantile(cost_inc, 0.95, q=0.95, na.rm = T),1), ")"),
            netdaly_averted = paste0(round(mean(netdaly_averted, na.rm = T),1), 
                                     " (", round(quantile(netdaly_averted, 0.05, q = 0.05, na.rm = T),1), " to ", 
                                     round(quantile(netdaly_averted, 0.95, q=0.95, na.rm = T),1), ")"),
            cf_any = pct(mean(cf_netdaly_any, na.rm = T)),
            cf_all = pct(mean(cf_netdaly_all, na.rm = T))) %>%  
  ungroup() %>% 
  select(source, inc_cost, netdaly_averted, cf_any, cf_all) %>% 
  mutate(age = "All") %>% 
  pivot_longer(cols = c(inc_cost, netdaly_averted, cf_any, cf_all), names_to = "var") %>% 
  pivot_wider(names_from = source, values_from = value)


x4 <- rbind(x2, x3)
write_csv(x4, paste0("./results/","t4_", y, ".csv"))
x4 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
x <- rbind(x1, x4)

```

``` {r table3b}

# t3vars_pct <- c("p_htn_true160", "p_hypert160", "p_dx_htn_true160", "p_on_tx_htn160", "p_ever_tx_htn160", "p_hypert_control160")
# 
# t3vars <- c(t3vars_pct)
# t3age <- c("18+", "25-44", "45-64", "65+")
# 
# sev1 <- df_sas %>% filter(year == y, age %in% t3age, var %in% t3vars) %>% 
#   group_by(var, age, source) %>%
#   summarize(mean_val = mean(value, na.rm = T),
#             q05 = quantile(value, 0.05, q = 0.05, na.rm = T), 
#             q95 = quantile(value, 0.95, q=0.95, na.rm = T)) %>%  
#   ungroup() %>% filter(!is.na(mean_val)) %>% 
#   mutate(mean_value = ifelse(var %in% t3vars_pct, paste0(pct(mean_val), " (", pct(q05), " to ", pct(q95), ")"), NA)) %>% 
#   arrange(match(var, t3vars)) %>% 
#   select(var, age, source, mean_value) %>% 
#   pivot_wider(names_from = source, values_from = mean_value)
# 
# # write_csv(sev1, paste0("./results/","sevhtn_", y, ".csv"))
# sev1 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

```


```{r cost-effectiveness table prep}
df_netdaly %>% 
  select(m_sbp_4564_23, p_htn_true_4564_23, p_diagnosed_hypert_4564_23, p_on_tx_htn_4564_23, p_hypert_control_4564_23, rate_dead_cvd_4564_23, prevalence1549_23) %>% 
  summary()

df_netdaly_params <- df_netdaly %>% 
  filter(year == y) %>% 
  mutate(sbp_cat = factor(ifelse(m_sbp_4564_23 <132, "<132",
                          ifelse(m_sbp_4564_23 >=132 & m_sbp_4564_23 <136, "132 to <136", 
                          ifelse(m_sbp_4564_23 >=136 & m_sbp_4564_23 <140, "136 to <140", 
                          ifelse(m_sbp_4564_23 >=140 , ">=140", NA)))),
                          levels = c("<132", "132 to <136", "136 to <140", ">=140"),
                          labels = c("<132", "132 to <136", "136 to <140", ">=140")),
         hiv_cat = factor(ifelse(prevalence1549_23 <0.05, "<5%",
                          ifelse(prevalence1549_23 >=0.05 & prevalence1549_23 <0.10, "5 to <10%", 
                          ifelse(prevalence1549_23 >=0.10 & prevalence1549_23 <0.15, "10 to <15%", 
                          ifelse(prevalence1549_23 >=0.15 , ">=15%", NA)))),
                          levels = c("<5%", "5 to <10%", "10 to <15%", ">=15%"),
                          labels = c("<5%", "5 to <10%", "10 to <15%", ">=15%")),
         htn_cat = factor(ifelse(p_htn_true_4564_23 <0.35, "<35%",
                          ifelse(p_htn_true_4564_23 >=0.35 & p_htn_true_4564_23 <0.43, "35 to <43%", 
                          ifelse(p_htn_true_4564_23 >=0.43 & p_htn_true_4564_23 <0.50, "43 to <50%", 
                          ifelse(p_htn_true_4564_23 >=0.50 , ">=50%", NA)))),
                          levels = c("<35%", "35 to <43%", "43 to <50%", ">=50%"),
                          labels = c("<35%", "35 to <43%", "43 to <50%", ">=50%")),
         dx_cat = factor(ifelse(p_diagnosed_hypert_4564_23 <0.22, "<22%",
                         ifelse(p_diagnosed_hypert_4564_23 >=0.22 & p_diagnosed_hypert_4564_23 <0.28, "22 to <28%", 
                         ifelse(p_diagnosed_hypert_4564_23 >=0.28 & p_diagnosed_hypert_4564_23 <0.36, "28 to <36%", 
                         ifelse(p_diagnosed_hypert_4564_23 >=0.36 , ">=36%", NA)))),
                         levels = c("<22%", "22 to <28%", "28 to <36%", ">=36%"),
                         labels = c("<22%", "22 to <28%", "28 to <36%", ">=36%")),
         tx_cat = factor(ifelse(p_on_tx_htn_4564_23  <0.04, "<4%",
                         ifelse(p_on_tx_htn_4564_23 >=0.04 & p_on_tx_htn_4564_23 <0.06, "4 to <6%", 
                         ifelse(p_on_tx_htn_4564_23 >=0.06 & p_on_tx_htn_4564_23 <0.09, "6 to <9%", 
                         ifelse(p_on_tx_htn_4564_23 >=0.09 , ">=9%", NA)))),
                         levels = c("<4%", "4 to <6%", "6 to <9%", ">=9%"),
                         labels = c("<4%", "4 to <6%", "6 to <9%", ">=9%")),
         ctrl_cat = factor(ifelse(p_hypert_control_4564_23 <0.02, "<2%",
                           ifelse(p_hypert_control_4564_23 >=0.02 & p_hypert_control_4564_23 <0.04, "2 to <4%", 
                           ifelse(p_hypert_control_4564_23 >=0.04 & p_hypert_control_4564_23 <0.06, "4 to <6%", 
                           ifelse(p_hypert_control_4564_23 >=0.06 , ">=6%", NA)))),
                           levels = c("<2%", "2 to <4%", "4 to <6%", ">=6%"),
                           labels = c("<2%", "2 to <4%", "4 to <6%", ">=6%")),
         cvd_cat = factor(ifelse(rate_dead_cvd_4564_23 < 0.4, "<400 per 100,000",
                          ifelse(rate_dead_cvd_4564_23 >=0.4 & rate_dead_cvd_4564_23 <0.5, "400 to <500 per 100,000", 
                          ifelse(rate_dead_cvd_4564_23 >=0.5 & rate_dead_cvd_4564_23 <0.6, "500 to <600 per 100,000", 
                          ifelse(rate_dead_cvd_4564_23 >=0.6 , ">=600 per 100,000", NA)))),
                           levels = c("<400 per 100,000", "400 to <500 per 100,000", "500 to <600 per 100,000", ">=600 per 100,000"),
                           labels = c("<400 per 100,000", "400 to <500 per 100,000", "500 to <600 per 100,000", ">=600 per 100,000")),
         setting_cvd_tx = factor(setting_cvd_tx),
         setting_cvd_tx_eff = factor(setting_cvd_tx_eff),
         setting_prob_htn_link = factor(setting_prob_htn_link)) %>% 
  select(country, source, cost_cat, year, cf_netdaly_any, cf_netdaly_all, sbp_cat, htn_cat, dx_cat, tx_cat, ctrl_cat, cvd_cat, setting_sbp_cal, setting_cvd_tx, setting_cvd_tx_eff, setting_cost_lowqual_cvd, setting_prob_htn_link, hiv_cat)

df_netdaly_paramsbase <- df_netdaly_params %>% filter(cost_cat == "Base case cost assumptions") 


```

## Table 5
Proportion of setting-scenarios where each hypertension policy is the most cost-effective over next 50 years (2024-2074), assuming a cost-effectiveness threshold of $500 USD per DALY averted

```{r table5}


z1 <- df_netdaly_params %>% 
  group_by(source, cost_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Cost scenarios") %>% 
  rename(prop = cost_cat)

# remainder only for cost scenarios = htn total
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, hiv_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "HIV prevalence among age 15-49")  %>% 
  rename(prop = hiv_cat)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cost_lowqual_cvd) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Cost of ineffective emergency CVD care compared to effective care")  %>% 
  rename(prop = setting_cost_lowqual_cvd)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cvd_tx_eff) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Proportion of acute CVD events receiving effective emergency care")  %>% 
  rename(prop = setting_cvd_tx_eff)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_cvd_tx) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Proportion of acute CVD events receiving emergency care")  %>% 
  rename(prop = setting_cvd_tx)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, setting_sbp_cal) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "SBP rise per decade after 2015",
         setting_sbp_cal = paste0(setting_sbp_cal*40, " mmHg"))  %>% 
  rename(prop = setting_sbp_cal)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, cvd_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "CVD mortality rate among adults aged 45-64")  %>% 
  rename(prop = cvd_cat)  %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, ctrl_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension control among adults aged 45-64")  %>% 
  rename(prop = ctrl_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, tx_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension treatment among adults aged 45-64")  %>% 
  rename(prop = tx_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, dx_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all))) %>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension diagnosis among adults aged 45-64")  %>% 
  rename(prop = dx_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, htn_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all)))%>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Hypertension prevalence among adults aged 45-64") %>% 
  rename(prop = htn_cat) %>% 
  rbind(z1)
z1 <- df_netdaly_paramsbase %>% 
  group_by(source, sbp_cat) %>% 
  summarize(n = n(),
            prop = pct(mean(cf_netdaly_all)))%>% 
  pivot_wider(names_from = source, values_from = prop) %>% 
  mutate(parameter = "Mean SBP among adults aged 45-64") %>% 
  rename(prop = sbp_cat) %>% 
  rbind(z1)

z1 <- z1 %>% select(parameter, prop, n, SOC, CCC, CHW)
write_csv(z1, paste0("./results/","cfparams_", y, ".csv"))
z1  %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
```


# Figures

## Figure 2. Hypertension Cascade among adults aged ≥18 years

```{r}
fig2 <- df_sas %>% 
  filter(year == y, age %in% c("18+", "45-64"), var %in% c("p_dx_htn_true", "p_on_tx_htn", "p_hypert_control")) %>% 
  mutate(var = factor(var, 
                      levels = c("p_dx_htn_true", "p_on_tx_htn", "p_hypert_control"),
                      labels = c("Diagnosis", "Treatment (current)", "Hypertension control"))) %>% 
  group_by(source, var, age) %>% 
  summarize(mean = mean(value), q05 = quantile(value, 0.05), q95 = quantile(value, 0.95)) %>% 
  mutate(lower = mean - q05,
         upper = q95 - mean)

fig2 %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)

fig2 %>% 
  ggplot(aes(y = mean, x = source, fill = source)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=q05, ymax=q95, x = source), width = 0.4, color = "#636363") +
    facet_wrap(~ age + var) +
    theme_classic(base_size = 16) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")

write_csv(fig2, paste0("./results/","figure1_", y, ".csv"))

```


## Figure 3. Cost-effectiveness of hypertension treatment policies
```{r icer}
plot_icer_base <- plot_icer %>% 
  rename(policy = source) %>% 
  filter(cost_cat == "Base case cost assumptions") %>% 
  mutate(icer_text = ifelse(is.na(icer2), "SOC", paste0(policy, "\n", "$", icer2, "/DALY")),
         nudge_y = ifelse(policy == "CCC", 6, 
                          ifelse(policy == "CHW", 2, NA)))

ccc_icer <- plot_icer_base %>% filter(policy == "CCC") %>% ungroup() %>% select(icer2)
chw_icer <- plot_icer_base %>% filter(policy == "CHW") %>% ungroup() %>% select(icer2)

# Create the overlayed plot
fig3 <- ggplot() +
  # First plot: Points from df_netdaly
  geom_point(data = df_netdaly %>% 
               rename(policy = source) %>% 
               filter(year == "2474", cost_cat == "Base case cost assumptions"),
             aes(x = ddaly_averted, y = cost_inc, color = policy), alpha = 0.4, size = 0.1) +
  # Axis lines at x=0 and y=0
  geom_hline(yintercept = 0, color = "#636363", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "#636363", linetype = "dashed") +
  # Second plot: Lines and points from plot_icer_base
  geom_point(data = plot_icer_base,
             aes(x = mean_ddaly, y = mean_cost), size = 2.5, alpha = 1, color = "black") +
  geom_line(data = plot_icer_base,
            aes(x = mean_ddaly, y = mean_cost),
            linewidth = 0.8) +
  geom_point(data = plot_icer_base,
             aes(x = mean_ddaly, y = mean_cost, color = policy), size = 1.5) +
  # ggrepel annotations
  geom_label_repel(data = plot_icer_base, 
                   aes(x = mean_ddaly, y = mean_cost, color = policy, label = icer_text), 
                   nudge_y = c(8, 5, 5),
                   nudge_x = c(-40, 170, 130),
                   fill = alpha("white", 0.5),
                   direction = "y",  # Keep labels in a vertical column
                   hjust = 0.5,  # Left-align the text
                   segment.size = 0.2,
                   force = 1,
                   min.segment.length = 0,
                   show.legend = FALSE) +
  # Shared labels, theme, and scales
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  labs(title = "Cost-effectiveness frontier",
       subtitle = "Per 10 million adults over 50-year time horizon",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  labs(color = "Policy") +
  theme_classic() +
  theme(
    plot.title = element_text(size = 16, face = "bold", color = "#636363"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363")
  ) +
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")

# Display the combined plot
print(fig3)

ggsave("results/fig3.pdf", plot = fig3, device = "pdf", width = 7.5, height = 5, units = "in", dpi = 600)

ggsave("results/fig3.eps", plot = fig3, device = "eps", width = 7.5, height = 5, units = "in", dpi = 600)

```

## Figure 4. Cost-effectiveness of hypertension policies at varying cost-effectiveness thresholds
```{r cf_all_graph}
knitr::opts_chunk$set(echo = FALSE, message = F, fig.height=20, fig.width=15)
fig4a <- df_netdaly_graph %>% filter(year == "2474", cost_cat == "Base case cost assumptions", ce_threshold >10) %>% 
  group_by(source, ce_threshold) %>% 
  summarize(prop = mean(cf_netdaly_all)) %>% 
  ggplot(aes(x = ce_threshold, y = prop, color=source)) +
  geom_line() +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1000)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10), labels = dollar, limits = c(0,1000)) + 
  labs(title = "A. Proportion of setting-scenarios where policy is cost-effective, \nby cost-effectiveness threshold",
       subtitle = "Over 50 year time horizon from 2024-2074",
       y = "Proportion of settings where policy leads to greatest net DALYs averted",
       x = "Cost-effectiveness threshold (USD/DALY averted)") +
  theme_classic() +
  theme(
    plot.title = element_text(size = 12, face = "bold", color = "#636363"),
    plot.subtitle = element_text(size = 9),
    legend.position = "none",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363"),
    axis.title = element_text(color = "#636363", size = 8)
  ) +
  scale_color_brewer(palette = "Dark2") +
  annotate("text", x=980, y=0.85, label= "CHW", color = "#7570B3", size = 4) +
  annotate("text", x=980, y=0.14, label= "CCC", color = "#D95F02", size = 4) +
  annotate("text", x=980, y=0.05, label= "SOC", color = "#1B9E77", size = 4) +
  annotate("text", x=100, y=0.94, 
           label = "Approximate lower income threshold, \ndomestic funding (e.g. Malawi)", color = "#636363", size = 2.5) +
  annotate("text", x=500, y=0.94, 
           label = "Approximate lower-middle income threshold, \ndomestic funding (e.g. Kenya)", color = "#636363", size = 2.5) +
  annotate("text", x = 500, y = 1, label = expression(bold("Primary analysis")), color = "#636363", size = 2.5) + 
  geom_segment(aes(x=500, y=0, xend=500, yend=0.9), linewidth = 0.2, linetype = "dashed", color = "#636363") +
  geom_segment(aes(x=100, y=0, xend=100, yend=0.9), linewidth = 0.2, linetype = "dashed", color = "#636363")
  
fig4b <- df_netdaly_distribution %>% 
  rename(policy = source) %>% 
  mutate(ce_threshold = as.numeric(ce_threshold)) %>% 
  filter(year == "2474", cost_cat == "Base case cost assumptions", ce_threshold >50) %>% 
  group_by(policy, ce_threshold) %>% 
  summarize(netdaly = median(netdaly_averted),
            quantile_05 = quantile(netdaly_averted, 0.05),
            quantile_95 = quantile(netdaly_averted, 0.95)) %>% 
  ggplot(aes(x = ce_threshold, fill = policy, color=policy)) +
  geom_line(aes(y = netdaly)) +
  geom_ribbon(aes(ymin = quantile_05, ymax = quantile_95), color = NA, show.legend = FALSE, alpha = 0.1) + 
  coord_cartesian(xlim = c(0,1000)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10), labels = dollar, limits = c(0,1000)) + 
  labs(title = "B. Net DALYs averted, by cost-effectiveness threshold",
       subtitle = "Median (90% range), estimated for population of 10 million adults over 50-year time horizon from 2024-2074",
       y = "Net DALYs averted (thousands)",
       x = "Cost-effectiveness threshold (USD/DALY averted)") +
  theme_classic() +
  theme(
    plot.title = element_text(size = 12, face = "bold", color = "#636363"),
    plot.subtitle = element_text(size = 9),
    legend.position = "bottom",
    text = element_text(color = "#636363"),
    axis.line = element_line(color = "#636363"),
    axis.ticks = element_line(color = "#636363"),
    axis.text = element_text(color = "#636363"),
    axis.title = element_text(color = "#636363", size = 8)
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_fill_brewer(palette = "Dark2")

# Combine the two figures vertically
fig4_combined <- fig4a / fig4b

# Display the combined plot
print(fig4_combined)

ggsave("results/fig4_combined.pdf", plot = fig4_combined, device = "pdf", width = 7.5, height = 10, units = "in", dpi = 600)
```

# Manuscript text
Year `r y`

## Methods

We evaluated `r df_sas_wide %>% filter(source == "SOC") %>% nrow()` setting-scenarios representing a range of settings across sub-Saharan Africa. Table 1 shows hypertension prevalence and care cascade parameters estimated by the model and from the literature. In 2015, the mean (90% range) model-estimated hypertension prevalence among adults aged 45-64 was `r t1_htn %>% filter(age == "45-64") %>% select(htn_mean)`. An estimated `r t1_dx %>% filter(age == "45-64") %>% select(dx_mean)` had ever been diagnosed, `r t1_tx %>% filter(age == "45-64") %>% select(tx_mean)` were on treatment, and `r t1_ctrl %>% filter(age == "45-64") %>% select(control_mean)` had controlled hypertension. Median (90% range) model-estimated HIV prevalence was `r t1_hiv %>% filter(age == "15-49") %>% select(hiv_mean)` among adults aged 15-49 years across setting-scenarios in 2015.



## Results

Over the next 50 years (2024-2074), the proportion of adults with hypertension aged 45-64 years who have received a hypertension diagnosis is expected to remain at `r x %>% filter(var == "p_dx_htn_true", age == "45-64") %>% select(SOC)` under current conditions (Table 3, Figure 1), with slight increases in prevalence over time due to improved survival among persons with hypertension (Appendix, Section 5). Improving clinic-based care without added screening (CCC policy) would only improve the proportion diagnosed to `r x %>% filter(var == "p_dx_htn_true", age == "45-64") %>% select(CCC)`, whereas additional CHW screening (CHW policy) would increase diagnosis to `r x %>% filter(var == "p_dx_htn_true", age == "45-64") %>% select(CHW)`.

The proportion currently on antihypertensive treatment among adults aged 45-64 with hypertension would remain low at `r x %>% filter(var == "p_on_tx_htn", age == "45-64") %>% select(SOC)` under standard of care, whereas the proportion currently on treatment  would increase to `r x %>% filter(var == "p_on_tx_htn", age == "45-64") %>% select(CCC)` with CCC implementation and `r x %>% filter(var == "p_on_tx_htn", age == "45-64") %>% select(CHW)` with CHW screening. 

With expanded screening, there is risk of overdiagnosis and overtreatment. In the CHW policy, we estimate that `r x %>% filter(var == "p_dx_htn_over", age == "18+") %>% select(CHW)` of normotensive adults would receive a hypertension diagnosis and `r x %>% filter(var == "p_on_tx_htn_over", age == "18+") %>% select(CHW)` would be on treatment, with prevalence increasing with age (`r x %>% filter(var == "p_dx_htn_over", age == "45-64") %>% select(CHW)` overdiagnosed and `r x %>% filter(var == "p_on_tx_htn_over", age == "45-64") %>% select(CHW)` overtreated among age ≥65). Estimated mean pre-treatment SBP among overdiagnosed individuals is `r x_over %>% filter(var == "m_sbp_max_over", age == "18+") %>% select(CHW)`, indicating that this phenomenon is expected to occur mostly among those near the treatment threshold (SBP ≥140 mmHg) and likely to benefit from treatment.

We project that hypertension control among those with true hypertension (SBP ≥140 mmHg) would remain low at `r x %>% filter(var == "p_hypert_control", age == "45-64") %>% select(SOC)` among adults aged 45-64 years under current standard hypertension treatment conditions. Implementing the CCC policy alone would increase the proportion of those with hypertension maintaining blood pressure control to `r x %>% filter(var == "p_hypert_control", age == "45-64") %>% select(CCC)` and CHW screening to `r x %>% filter(var == "p_hypert_control", age == "45-64") %>% select(CHW)`.

### Cardiovascular disease outcomes

Incident IHD events are projected to be `r x %>% filter(var == "rate_ihd_modsev", age == "45-64") %>% select(SOC)` per 100 person-years in all adults aged 45-64 under standard of care conditions with expected relative risk of `r x %>% filter(var == "rate_ihd_modsev_rr", age == "45-64") %>% select(CCC)` with CCC implementation and `r x %>% filter(var == "rate_ihd_modsev_rr", age == "45-64") %>% select(CHW)` with CHW screening. Stroke incidence is projected to be `r x %>% filter(var == "rate_cva_modsev", age == "45-64") %>% select(SOC)` per 100 person-years in adults aged 45-64 under standard of care conditions with expected relative risk of `r x %>% filter(var == "rate_cva_modsev_rr", age == "45-64") %>% select(CCC)` with CCC implementation and `r x %>% filter(var == "rate_cva_modsev_rr", age == "45-64") %>% select(CHW)` with CHW screening.  Projected relative risk for CVD mortality among all adults aged 18 and above is `r x %>% filter(var == "rate_dead_cvd_rr", age == "18+") %>% select(CCC)` with CCC and `r x %>% filter(var == "rate_dead_cvd_rr", age == "18+") %>% select(CHW)` with CHW policies. CCC implementation alone is expected to avert a mean of `r x %>% filter(var == "ddaly_averted") %>% select(CCC)` thousand DALYs per year for a population of 10 million persons aged 15 and older, whereas the projected health benefits of CHW screening are more than 3-fold greater (`r x %>% filter(var == "ddaly_averted") %>% select(CHW)` thousand DALYs averted annually). 

### Costs and cost-effectiveness

Mean incremental costs compared to standard care, discounted over the 50 year time horizon, are $`r x %>% filter(var == "inc_cost") %>% select(CCC)` million USD for chronic care clinic implementation and $`r x %>% filter(var == "inc_cost") %>% select(CHW)` million USD for additional CHW screening, scaled to a total population size of 10 million adults. The incremental cost-effectiveness ratio (ICER) was $`r plot_icer %>% ungroup() %>% filter(cost_cat == "Base case cost assumptions", source =="CCC") %>% select(icer2)`/DALY averted for CCC and $`r plot_icer %>% ungroup() %>% filter(cost_cat == "Base case cost assumptions", source =="CHW") %>% select(icer2)`/DALY averted for CHW policies (Figure 2). Using a cost-effectiveness threshold of $500 USD/DALY averted, the CHW policy was cost-effective in `r x %>% filter(var == "cf_all") %>% select(CHW)` of scenarios, the CCC policy in `r x %>% filter(var == "cf_all") %>% select(CCC)`, and neither policy was cost-effective in `r x %>% filter(var == "cf_all") %>% select(SOC)` of scenarios (Table 4). 

Stratifying on baseline setting-scenario characteristics (Table 5), community-wide CHW screening was more cost-effective in settings with a greater baseline burden of hypertension and CVD mortality. Cost-effectiveness of the clinic-based CCC policy increased with greater HIV prevalence, though CHW screening remained the cost-effective strategy even in settings with the highest HIV prevalence. Cost-effectiveness of CHW screening increased with greater acute care utilization for CVD events (and thus higher acute care costs), though remained cost-effective in the majority of setting-scenarios (`r z1 %>% filter(parameter == "Proportion of acute CVD events receiving emergency care" & prop == "0.5") %>% select(CHW)`) where only 20% of people sought emergency care following an acute CVD event. 

We also evaluated several alternative cost scenarios (Table 5). CHW screening (with CCC) was most sensitive to higher cost scenarios. CHW screening was cost-effective in `r z1 %>% filter(parameter == "Cost scenarios" & prop == "Drug costs 200% of base") %>% select(CHW)` of setting-scenarios where drug costs were doubled, indicating settings where high-quality drugs could not be obtained at generic prices. CHW screening was be cost-effective in only `r z1 %>% filter(parameter == "Cost scenarios" & prop == "Clinic costs 200% of base") %>% select(CHW)` of setting-scenarios where clinical costs were doubled, indicating settings with higher opportunity costs of additional clinic visits. ICERs for alternative cost scenarios can be found in the Appendix (Section 5).

In sensitivity analyses, we evaluate cost-effectiveness of each policy under varying cost-effectiveness thresholds, reporting the proportion of setting-scenarios where each policy is cost-effective as defined by incurring the fewest net DALYs at a given cost-effectiveness threshold (Figure 4A). When the presumed cost-effectiveness threshold is decreased to $300 USD per DALY averted, the CCC policy without community screening was cost-effective in `r df_netdaly_graph_summ %>% ungroup() %>% filter(source == "CCC", ce_threshold == 300) %>% select(pct)` of modeled scenarios. When the cost-effectiveness threshold is further decreased to $100 USD per DALY averted, a threshold that is likely affordable with domestic funding in most countries in sub-Saharan Africa, CCC implementation was the cost-effective policy in `r df_netdaly_graph_summ %>% ungroup() %>% filter(source == "CCC", ce_threshold == 100) %>% select(pct)` of settings. Figure 4B demonstrates the median and 90% range of net DALYs averted across cost-effectiveness thresholds. It is apparent from this figure that for very low cost-effectiveness thresholds approaching $100 USD/DALY averted, the CHW policy is associated with a large negative number of net DALYs averted – suggesting large opportunity costs for implementing the CHW policy in settings with a very low cost-effectiveness threshold.


