---
title: "SEARCH Hypertension Modelling with HIV Synthesis"
author: "Matt Hickey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    reference_docx: template.docx
always_allow_html: true

---

```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(ggrepel)

options(tinytex.verbose = TRUE)
options(scipen = 999)


knitr::opts_chunk$set(echo = FALSE, fig.height=7, fig.width=10, dpi=300)
knitr::opts_knit$set(root.dir = '~/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration')

pct <- function(x) {
  y <- paste0(round((x*100),0),"%")
  return(y)
}

load("~/Library/CloudStorage/Box-Box/1.sapphire_modelling/calibration/SynthesisHTN_105.RData")

```



# Comparison of model output in 2015 to data from the literature
Based on `r nrow(df_sas_wide)/3` model runs

## Definitions
SOC = Standard of Care (Synthesis model output)   
GBD = Global Burden of Disease data

## Data Sources
Hypertension prevalence, diagnosis, treatment, and control using STEPS survey data from 15 countries in sub-Saharan Africa (2005-2015; Geldsetzer Lancet 2019)

Systolic blood pressure for men and women based on 2015 Global Burden of Disease survey data as published in Forouzanfar MH, Liu P, Roth GA, et al. Global Burden of Hypertension and Systolic Blood Pressure of at Least 110 to 115 mm Hg, 1990-2015. JAMA. 2017;317(2):165-182. doi:10.1001/jama.2016.19043


## SBP Increase with Age

```{r graph_sbp_w}
df_sbp %>% filter(sex == "Female", source %in% c("GBD 2015", "SOC"), year == "15") %>% 
    ggplot(aes(age,sbp, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(110,160)) +
    labs(x = "Age", y = "Mean SBP", title = "Mean SBP by age (Women)", subtitle = "in 2015") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
      )
#ggsave(paste0("05sbp_w_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

```{r graph_sbp_m}
 df_sbp %>% filter(sex == "Male", source %in% c("GBD 2015", "SOC"), year == "15") %>% 
    ggplot(aes(age,sbp, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(110,160)) +
    labs(x = "Age", y = "Mean SBP", title = "Mean SBP by age (Men)", subtitle = "in 2015") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

  
  #ggsave(paste0("06sbp_m_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

## Hypertension Prevalence
Hypertension defined as true SBP >=140 mmHg, regardless of whether measured.

```{r graph_htn}

df_htn %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+"), source %in% c("Geldsetzer", "SOC"), year == "15") %>% 
  ggplot(aes(age,htn, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    labs(x = "Age", y = "Proportion with hypertension", title = "Hypertension prevalence", subtitle = "in 2015") +
    coord_cartesian(ylim = c(0,NA)) +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom")

# df_sevhtn %>% filter(age != "18+", source %in% c("SEARCH (Kenya/Uganda)", "NIDS (South Africa)", "SOC"), year == "15") %>% 
#   ggplot(aes(age, sevhtn, color=source)) +
#     geom_boxplot() +
#     theme_minimal(base_size = 14) +
#     labs(x = "Age", y = "Proportion with severe hypertension (SBP ≥160)", title = "Severe hypertension prevalence (SBP≥160 mmHg)", subtitle = "In 2015") +
#     coord_cartesian(ylim = c(0,NA)) +
#     theme(plot.title = element_text(size = 18, face = "bold"),
#       legend.position = "bottom")

  #ggsave(paste0("01htn_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```


## Hypertension Diagnosis 
* Measured SBP value if measured: true SBP + random error with SD 10 mmHg

* Hypertension diagnosis made if any of the following:
  1. measured SBP >=140 mmHg on two consecutive clinic visits
  2. measured SBP >=160 mmHg once
  3. started on antihypertensive medication (see Hypertension Treatment section below)

```{r graph_dx}
df_dx %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+"), source %in% c("Geldsetzer", "SOC"), year == "15") %>% 
  ggplot(aes(age,dx, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion diagnosed", title = "Hypertension diagnosis", subtitle = "in 2015") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom")

  #ggsave(paste0("02dx_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```


## Hypertension Treatment


```{r graph_tx_curr}
df_tx_current %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+", "18+", "All"), source %in% c("Geldsetzer", "SOC"), year == "15") %>% 
  ggplot(aes(age,tx, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,0.5)) +
    labs(x = "Age", y = "Proportion currently on treatment", title = "Current hypertension treatment", subtitle = "in 2015",
         caption = "Defined as currently taking antihypertensive medications") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom")

  #ggsave(paste0("03tx_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

<span style="color: blue;"> **Note:** The model considers treatment to be on medications and adherent to those medications. Real-world data is based on self-report of treatment and may include some who report taking medications but are non-adherent. </span>

Geldsetzer Lancet 2019 includes country-specific data on `r df_ssa_txctrl %>% nrow()` countries in Africa with data on medication treatment and reports an overall prevalence of pharmacologic hypertension treatment of 13.0% (95% CI 12.0-14.2%) when weighting countries by population size.

```{r htn_tx_data}
# df_ssa_txctrl %>% select(country, tx, tx_95ci) %>% arrange(tx) %>% mutate(tx = pct(tx)) %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
```


```{r graph_tx_ever}
 df_tx_ever %>% filter(source %in% c("Geldsetzer", "SOC"), year == "15") %>% ggplot(aes(age,tx, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,0.5)) +
    labs(x = "Age", y = "Proportion ever on treatment", title = "Ever on hypertension treatment", 
         subtitle = "in 2015",
         caption = "Defined as ever taking antihypertensive medications") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom")

  #ggsave(paste0("03tx_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```


## Hypertension Control

* Control defined as current true SBP <140 among persons with maximum SBP >=140 (pre-treatment)

```{r graph_ctrl}
 df_ctrl %>% filter(age %in% c("25-34", "35-44", "45-54", "55-64", "65+", "18+", "All"), source %in% c("Geldsetzer", "SOC"), year == "15") %>% 
  ggplot(aes(age,control, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion with controlled BP", title = "Hypertension control", subtitle = "in 2015") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom")

  #ggsave(paste0("04ctrl_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

Geldsetzer Lancet 2019 includes country-specific data on `r df_ssa_txctrl %>% nrow()` countries in Africa with data on hypertension control and reports an overall prevalence of hypertension control (<140/90 mmHg) of 4.3% (95% CI 3.6- 4.9%). 

```{r htn_ctrl_data}
# df_ssa_txctrl %>% select(country, control, control_95ci) %>% arrange(control) %>% mutate(control = pct(control)) %>% kable(booktabs = T) %>% kable_styling(font_size = 12, bootstrap_options = c("striped", "hover", "condensed"), position = "center", full_width = FALSE)
```


## CVD Events

**Data source:** 
Global Burden of Disease Collaborative Network.
Global Burden of Disease Study 2019 (GBD 2019) Results.
Seattle, United States: Institute for Health Metrics and Evaluation (IHME), 2020.
Available from https://vizhub.healthdata.org/gbd-results/.

### Incidence of Ischemic Heart Disease

Incidence of ischemic heart disease (angina and myocardial infarction(MI)). We assume that angina/silent MI are under-ascertained, thus we compare incidence only of moderate/severe MI to available incidence data.

```{r}
df_cvd_inc %>% filter(cause == "Ischemic heart disease", sex == "Male") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Ischemic Heart Disease",
         subtitle = "in 2015; Men",
         y = "Incident ischemic heart disease per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

df_cvd_inc %>% filter(cause == "Ischemic heart disease", sex == "Female") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Ischemic Heart Disease",
         subtitle = "in 2015; Women",
         y = "Incident ischemic heart disease per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

  
```


### Prevalence of Ischemic Heart Disease
Defined as any prior history of ischemic heart disease among living adults.
```{r}

df_cvd_prev %>% filter(sex == "Male", cause == "Ischemic heart disease") %>%
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Prevalence of Ischemic Heart Disease",
         subtitle = "in 2015; Men",
         y = "Prevalence of ischemic heart disease per 100 persons", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

df_cvd_prev %>% filter(sex == "Female", cause == "Ischemic heart disease") %>%
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Prevalence of Ischemic Heart Disease",
         subtitle = "in 2015; Women",
         y = "Prevalence of ischemic heart disease per 100 persons", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )
  
```

### Incidence of Stroke

We assume that mild strokes under-ascertained and thus compare incidence only of moderate/severe stroke to available incidence data.

```{r}
df_cvd_inc %>% filter(sex == "Male", cause == "Stroke") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Stroke ",
         subtitle = "in 2015; Men",
         y = "Incident stroke per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

df_cvd_inc %>% filter(sex == "Female", cause == "Stroke") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Stroke",
         subtitle = "in 2015; Women",
         y = "Incident stroke per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

  
```


### Prevalence of Stroke
Defined as any prior history of stroke among living adults.

```{r}
df_cvd_prev %>% filter(sex == "Male", cause == "Stroke") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Prevalence of Stroke",
         subtitle = "in 2015; Men",
         y = "Prevalence of stroke per 100 persons", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

df_cvd_prev %>% filter(sex == "Female") %>% 
  ggplot(aes(x = age, y = value, color = region)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Prevalence of Stroke",
         subtitle = "in 2015; Women",
         y = "Prevalence of stroke per 100 persons", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )


  
```


## CVD Mortality
Mortality resulting from ischemic heart disease or stroke.

```{r}
df_cvd_death <- df_cvd_death %>% 
    mutate(source = ifelse(source == "SSA", "GBD 2015", 
                         ifelse(source == "SOC", "SOC", source)),
           source = factor(source, levels = c("SOC", "GBD 2015"))) 

df_cvd_death %>% filter(sex == "Male") %>% 
  ggplot(aes(x = age, y = cvd_death_rate, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "CVD Mortality",
         subtitle = "in 2015; Men",
         y = "CVD mortality per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

df_cvd_death %>% filter(sex == "Female") %>% 
  ggplot(aes(x = age, y = cvd_death_rate, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "CVD Mortality",
         subtitle = "in 2015; Women",
         y = "CVD mortality per 100 person-years", x = "Age") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    )

```


# Section 5: Supplemental Results

Hypertension care cascade for CCC and CHW policy scenarios compared to standard of care. Model estimates averaged over 2024-2074.

## Prevalence
```{r graph_htn_int}

df_sas %>% filter(var == "p_htn_true", age %in% c("18+", "25-34", "35-44", "45-54", "55-64", "65+"), year == "2474", sex == "All") %>% 
  ggplot(aes(age, value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    labs(x = "Age", y = "Proportion with hypertension", title = "Hypertension prevalence", subtitle = "Average from 2024-2074") +
    coord_cartesian(ylim = c(0,NA)) +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "p_htn_true160", year == "2474", sex == "All") %>% 
  ggplot(aes(age, value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    labs(x = "Age", y = "Proportion with severe hypertension (SBP ≥160)", title = "Severe hypertension prevalence (SBP ≥160 mmHg)", subtitle = "Average from 2024-2074, max SBP (regardless of current BP control)") +
    coord_cartesian(ylim = c(0,NA)) +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

  #ggsave(paste0("01htn_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

## Diagnosis
```{r graph_dx_int}
df_sas %>% filter(var == "p_diagnosed_hypert", age %in% c("25-34", "35-44", "45-54", "55-64", "65+"), year == "2474", sex == "All") %>% 
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion diagnosed", title = "Hypertension diagnosis", subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "p_dx_htn_true160", year == "2474", sex == "All") %>% 
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion diagnosed", title = "Hypertension diagnosis among those with severe hypertension", 
         subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

  #ggsave(paste0("02dx_", Sys.Date(),".pdf"), path = "plots/", width = 10.65, height = 7.68, units = "in")
```

**Note:** Diagnosis can be >100% because the denominator is the proportion with true hypertension (SBP >=140) and the numerator is all with diagnosed hypertension including those who were overdiagnosed (measured BP >=140 but true BP <140). See additional graphs for overdiagnosis below.


```{r graph_dx_over}
df_sas %>% filter(var == "p_dx_htn_over", year == "2474", sex == "All") %>%
  ggplot(aes(age, value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion overdiagnosed", 
         title = "Overdiagnosis", 
         subtitle = str_wrap("Proportion of normotensive individuals (true SBP <140) who received a hypertension diagnosis (Average from 2024-2074)", 100)) +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

```

```{r graph_dx_true}
df_sas %>% filter(var == "p_dx_htn_true", year == "2474", sex == "All") %>%
  ggplot(aes(age, value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion with true SBP >=140 who were diagnosed", title = "True hypertension diagnosis", 
         subtitle = str_wrap("Proportion with of those with true SBP >=140 who were diagnosed with hypertension (Average from 2024-2074)",100)) +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

```


## Treatment
```{r graph_tx_curr_int}
df_sas %>% filter(var == "p_on_tx_htn", age %in% c("25-34", "35-44", "45-54", "55-64", "65+"), year == "2474", sex == "All") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion currently on treatment", title = "Hypertension treatment (current) among those with true hypertension", subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

# df_sas %>% filter(var == "p_on_tx_htn160", year == "2474", sex == "All") %>%
#   ggplot(aes(age,value, color=source)) +
#     geom_boxplot() +
#     theme_minimal(base_size = 14) +
#     coord_cartesian(ylim = c(0,NA)) +
#     labs(x = "Age", y = "Proportion currently on treatment", title = "Hypertension treatment (current) among those with severe hypertension", 
#          subtitle = "Average from 2024-2074") +
#     theme(plot.title = element_text(size = 18, face = "bold"),
#       legend.position = "bottom") +
#     scale_color_brewer(palette = "Dark2")

```

```{r graph_tx_ever_int}
df_sas %>% filter(var == "p_ever_tx_htn", age %in% c("18+", "25-44", "45-64", "65+"), year == "2474", sex == "All") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion ever on treatment", title = "Hypertension treatment (ever) among those with true hypertension", 
         subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

```

### Overtreatment
```{r}
df_sas %>% filter(var == "p_on_tx_htn_over", year == "2474", sex == "All") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion currently on treatment", title = "Hypertension treatment (current) among those who do not have hypertension", subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")
```


## HTN control
```{r graph_ctrl_int}
df_sas %>% filter(var == "p_hypert_control", age %in% c("25-34", "35-44", "45-54", "55-64", "65+"), year == "2474", sex == "All") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion with controlled BP", title = "Hypertension control", subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "p_hypert_control160", year == "2474", sex == "All") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(x = "Age", y = "Proportion with controlled BP", title = "Hypertension control among those with severe hypertension", subtitle = "Average from 2024-2074") +
    theme(plot.title = element_text(size = 18, face = "bold"),
      legend.position = "bottom") +
    scale_color_brewer(palette = "Dark2")

```

## SBP Increase with Age
```{r graph_sbp_int}
df_sas %>% filter(var == "m_sbp", year == "2474", sex == "Female") %>%
  ggplot(aes(age,value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(110,160)) +
    labs(x = "Age", y = "Mean SBP", title = "Mean SBP by age (Women)", subtitle = "Average from 2024-2074") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
      ) +
    scale_color_brewer(palette = "Dark2")
```

```{r graph_sbp_m_int}
df_sas %>% filter(var == "m_sbp", year == "2474", sex == "Male") %>%
  ggplot(aes(age,value, color=source)) +
      geom_boxplot() +
      theme_minimal(base_size = 14) +
      coord_cartesian(ylim = c(110,160)) +
      labs(x = "Age", y = "Mean SBP", title = "Mean SBP by age (Men)", subtitle = "Average from 2024-2074") +
      theme(
        plot.title = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

```

## CVD Event incidence

#### Incident Ischemic Heart Disease Events
```{r}
df_sas %>% filter(var == "rate_ihd_modsev", year == "2474", sex == "Male", age != "All") %>% 
  ggplot(aes(x = age, y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Ischemic Heart Disease",
         subtitle = "Men; Average from 2024-2074",
         y = "Incident ischemic heart disease per 100 person-years", x = "Age",
         caption = "moderate/severe events only") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_ihd_modsev", year == "2474", sex == "Female", age != "All") %>% 
  ggplot(aes(x = age, y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Ischemic Heart Disease",
         subtitle = "Women; Average from 2024-2074",
         y = "Incident ischemic heart disease per 100 person-years", x = "Age",
         caption = "moderate/severe events only") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "n_ihd_diff", year == "2474") %>% 
  ggplot(aes(y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Annual Ischemic Heart Disease events averted",
         subtitle = "Average from 2024-2074; Standardized to population size of 10 million adults in 2023",
         y = "Annual heart attacks averted among adults ≥18 years",
         caption = "moderate/severe events only") +
  scale_x_continuous(breaks = NULL) +
  theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_manual(values = c("#D95F02", "#7570B3"))

```

#### Incident Stroke
```{r}
df_sas %>% filter(var == "rate_cva_modsev", year == "2474", sex == "Male", age != "All") %>% 
  ggplot(aes(x = age, y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Stroke",
         subtitle = "Men; Average from 2024-2074",
         y = "Incident stroke per 100 person-years", x = "Age",
         caption = "moderate/severe events only") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_cva_modsev", year == "2474", sex == "Female", age != "All") %>% 
  ggplot(aes(x = age, y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Incidence of Stroke",
         subtitle = "Women; Average from 2024-2074",
         y = "Incident stroke per 100 person-years", x = "Age",
         caption = "moderate/severe events only") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "n_cvd_diff", year == "2474") %>% 
  ggplot(aes(y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Annual stroke events averted",
         subtitle = "Average from 2024-2074; Standardized to population size of 10 million adults in 2023",
         y = "Annual strokes averted among all adults ≥18 years",
         caption = "moderate/severe events only") +
  scale_x_continuous(breaks = NULL) +
  theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_manual(values = c("#D95F02", "#7570B3"))

```

## CVD Mortality

```{r graph_mortality}

df_sas %>% filter(var == "n_dead_cvd", year == "2474", sex == "All", age == "All") %>%
  ggplot(aes(y = value, color = source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs( y = "Number of CVD deaths", title = "Number of CVD deaths per year", 
          subtitle = "Average from 2024-2074; Standardized to population size of 10 million adults in 2023") +
  scale_x_continuous(breaks = NULL) +
    theme(
      plot.title = element_text(size = 20, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "n_dead_cvd_diff", year == "2474") %>% 
  ggplot(aes(y = value, color = source)) +
  geom_boxplot() +
  theme_minimal(base_size = 14) +
    labs(title = "Average annual CVD deaths averted from 2024-2074",
         subtitle = "Average from 2024-2074; Standardized to population size of 10 million adults in 2023",
         y = "Annual CVD deaths averted among adults ≥18 years") +
  scale_x_continuous(breaks = NULL) +
  theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_manual(values = c("#D95F02", "#7570B3"))

df_sas %>% filter(var == "rate_dead_cvd", year == "2474", sex == "All", age !="All") %>%
  ggplot(aes(age, value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    labs(title = "CVD mortality rate",
         subtitle = "Average from 2024-2074",
         y = "CVD mortality per 100 person-years") +
    coord_cartesian(ylim = c(0,NA)) +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_dead_hivneg_cvd", year == "2474", sex == "All", age == "18+") %>%
  ggplot(aes(y = value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(title = "CVD mortality rate among people without HIV",
         subtitle = "Average from 2024-2074",
         y = "CVD mortality rate per 100 person-years") +
  scale_x_continuous(breaks = NULL) +
    theme(
      panel.grid.major.x = element_blank(),
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_dead_hivpos_cvd", year == "2474", sex == "All", age == "18+") %>%
  ggplot(aes(y = value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(title = "CVD mortality rate among people with HIV",
         subtitle = "Average from 2024-2074",
         y = "CVD mortality rate per 100 person-years") +
  scale_x_continuous(breaks = NULL) +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_dead_hivneg_ac", year == "2474", sex == "All", age == "18+") %>%
  ggplot(aes(y = value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(title = "All-cause mortality rate among people without HIV",
         subtitle = "Average from 2024-2074",
         y = "All-cause mortality rate per 100 person-years") +
  scale_x_continuous(breaks = NULL) +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

df_sas %>% filter(var == "rate_dead_hivpos_ac", year == "2474", sex == "All", age == "18+") %>%
  ggplot(aes(y = value, color=source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs(title = "All-cause mortality rate among people with HIV",
         subtitle = "Average from 2024-2074",
         y = "All-cause mortality rate per 100 person-years") +
  scale_x_continuous(breaks = NULL) +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

```

## Cost

Cost assumptions (in USD):

* Community health worker screening: $3/person screened (estimates from SEARCH)
* Transportation voucher: $5/person linked (Hickey 2022)
* Clinic visits: $20/visit if uncontrolled and $10/visit if controlled (Shade 2021, Shiri 2021)
*	Fixed clinic training costs for CCC and CHW policies: $0.96 million USD per 10 million adult population
* HTN medications (90-day supply) (Resolve to Save Lives 2022)
  * Med 1 & 2: $1.5
  * Med 3: $3
* Acute MI/CVA treatment (Subramanian 2019)
  * MI: $2270
  * CVA: $2420
  * cost of acute care that is not effective (poor-quality):
    *	MI: $567.5 / $1135 / $2270
    *	CVA: $605 / $1210 / $2420
    *	we assume that some poor quality care may be due in part to limited staffing, diagnostic equipment, and medications - and therefore may also cost less. In other cases, similar interventions/diagnostic tests may be undertaken, though the effectiveness will be lower due to delays in care. We assume that such care for acute MI/CVA may cost lower than the cost of effective acute care (sampled from 25%, 50%, and 100% of the cost of effective care)


```{r cost}
df_sas %>% filter(year == "2474", var %in% c("dhtn_cost_scr", "dhtn_cost_clin", "dhtn_cost_drug", "dhtn_cost_cvd", "dhtn_cost_total")) %>%
    mutate(var = factor(var, 
                        levels = c("dhtn_cost_scr", "dhtn_cost_clin", "dhtn_cost_drug", "dhtn_cost_cvd", "dhtn_cost_total"),
                        labels= c("scr", "clin", "drug", "cvd", "total htn"))) %>% 
  ggplot(aes(var, value, color = source)) +
    geom_boxplot() +
    theme_minimal(base_size = 14) +
    coord_cartesian(ylim = c(0,NA)) +
    labs( y = "Cost in millions of USD (discounted)", title = "Average annual hypertension costs", 
          subtitle = "Average from 2024-2074; Standardized to population size of 10 million adults in 2023", x = "Cost category") +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_text(size = 16),
      legend.position = "bottom"
    ) +
    scale_color_brewer(palette = "Dark2")

```

Note that CVD costs vary widely because we sample from a range of CVD care utilization and cost in the main model, in addition to sensitivity analyses with different cost scenarios (Table 5 in the main text).

## Cost-effectiveness

### Cost-effectiveness frontier
```{r icer}

plot_icer <- plot_icer %>% 
  mutate(icer_text = ifelse(is.na(icer2), NA, paste0("$", icer2, "/DALY")),
         nudge_y = ifelse(source == "CCC", 6, 
                          ifelse(source == "CHW", 0, NA)))

plot_icer_clinic <- plot_icer %>% 
  filter(cost_cat %in% c("Clinic costs 50% of base", "Base case cost assumptions", "Clinic costs 200% of base"))
plot_icer_drug <- plot_icer %>% 
  filter(cost_cat %in% c("Drug costs 50% of base", "Base case cost assumptions", "Drug costs 200% of base"))
plot_icer_screen <- plot_icer %>% 
  filter(cost_cat %in% c("Screening costs 50% of base", "Base case cost assumptions", "Screening costs 200% of base")) %>% mutate(icer_text = ifelse(source != "CHW" & cost_cat != "Base case cost assumptions", NA, icer_text))

plot_icer_clinic %>% 
  ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
  geom_line() +
  geom_point() +
  annotate("text", x=13, y=12.5, label= "Chronic Care Clinic") +
  annotate("text", x=62, y=21, label= "CHW Screening") +
  geom_label_repel(aes(label = ifelse(is.na(icer_text), NA, icer_text)), 
                   nudge_y = plot_icer_clinic$nudge_y,
                   nudge_x = -10,
                   direction = "y",  # Keep labels in a vertical column
                   hjust = 0,  # Left-align the text
                   segment.size = 0.2,
                   force = 1,
                   min.segment.length = 0,
                   show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
  labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
       subtitle = "Alternative assumptions about clinic costs",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    legend.position = "bottom"
  ) +
  scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))

plot_icer_drug %>% 
  ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
  geom_line() +
  geom_point() +
  annotate("text", x=13, y=12.5, label= "Chronic Care Clinic") +
  annotate("text", x=62, y=21, label= "CHW Screening") +
  geom_label_repel(aes(label = ifelse(is.na(icer_text), NA, icer_text)), 
                   nudge_y = plot_icer_drug$nudge_y,
                   nudge_x = -10,
                   direction = "y",  # Keep labels in a vertical column
                   hjust = 0,  # Left-align the text
                   segment.size = 0.2,
                   force = 1,
                   min.segment.length = 0,
                   show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
  labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
       subtitle = "Alternative assumptions about drug costs",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    legend.position = "bottom"
  ) +
  scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))

plot_icer_screen %>% 
  ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
  geom_line() +
  geom_point() +
  annotate("text", x=13, y=12.5, label= "Chronic Care Clinic") +
  annotate("text", x=62, y=21, label= "CHW Screening") +
  geom_label_repel(aes(label = ifelse(is.na(icer_text), NA, icer_text)), 
                   nudge_y = plot_icer_screen$nudge_y,
                   nudge_x = -10,
                   direction = "y",  # Keep labels in a vertical column
                   hjust = 0,  # Left-align the text
                   segment.size = 0.2,
                   force = 1,
                   min.segment.length = 0,
                   show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
  labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
       subtitle = "Alternative assumptions about screening costs",
       y = "Annual incremental cost (millions $USD)",
       x = "Annual DALYs averted (thousands)") +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    legend.position = "bottom"
  ) +
  scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))



```


```{r}
# old cost-effectiveness frontier text
# plot_icer %>% 
#   filter(cost_cat %in% c("Clinic costs 50% of base", "Base case cost assumptions", "Clinic costs 200% of base")) %>% 
#   ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
#   geom_line() +
#   geom_point() +
#   annotate("text", x=0, y=1, label= "SOC") +
#   annotate("text", x=15, y=5, label= "Chronic Care Clinic") +
#   annotate("text", x=15, y=4, label= "$28/DALY", color = "#08306B") +
#   annotate("text", x=15, y=3, label= "$13/DALY", color = "#2171B5") +
#   annotate("text", x=15, y=2, label= "$6/DALY", color = "#6BAED6") +
#   annotate("text", x=65, y=21, label= "CHW Screening") +
#   annotate("text", x=65, y=20, label= "$587/DALY", color = "#08306B") +
#   annotate("text", x=65, y=19, label= "$381/DALY", color = "#2171B5") +
#   annotate("text", x=65, y=18, label= "$278/DALY", color = "#6BAED6") +
#   theme_minimal(base_size = 14) +
#   coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
#   labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
#        subtitle = "Alternative assumptions about clinic costs",
#        y = "Annual incremental cost (millions $USD)",
#        x = "Annual DALYs averted (thousands)") +
#   theme(
#     plot.title = element_text(size = 16, face = "bold"),
#     axis.title.y = element_text(size = 14),
#     axis.title.x = element_text(size = 14),
#     legend.position = "bottom"
#   ) +
#   scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))
# 
# plot_icer %>% 
#   filter(cost_cat %in% c("Drug costs 50% of base", "Base case cost assumptions", "Drug costs 200% of base")) %>% 
#   ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
#   geom_line() +
#   geom_point() +
#   annotate("text", x=0, y=1, label= "SOC") +
#   annotate("text", x=15, y=7, label= "Chronic Care Clinic") +
#   annotate("text", x=15, y=6, label= "$160/DALY", color = "#08306B") +
#   annotate("text", x=15, y=5, label= "$13/DALY", color = "#2171B5") +
#   annotate("text", x=15, y=4, label= "$-60/DALY (cost-saving)", color = "#6BAED6") +
#   annotate("text", x=65, y=21, label= "CHW Screening") +
#   annotate("text", x=65, y=20, label= "$532/DALY", color = "#08306B") +
#   annotate("text", x=65, y=19, label= "$381/DALY", color = "#2171B5") +
#   annotate("text", x=65, y=18, label= "$306/DALY", color = "#6BAED6") +
#     coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
#   theme_minimal(base_size = 14) +
#   labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
#        subtitle = "Alternative assumptions about drug costs",
#        y = "Annual incremental cost (millions $USD)",
#        x = "Annual DALYs averted (thousands)") +
#   theme(
#     plot.title = element_text(size = 16, face = "bold"),
#     axis.title.y = element_text(size = 14),
#     axis.title.x = element_text(size = 14),
#     legend.position = "bottom"
#   ) +
#    scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))
# 
# plot_icer %>% 
#   filter(cost_cat %in% c("Screening costs 50% of base", "Base case cost assumptions", "Screening costs 200% of base")) %>% 
#   ggplot(aes(x = mean_ddaly, y = mean_cost, color = cost_cat)) +
#   geom_line() +
#   geom_point() +
#   annotate("text", x=0, y=1, label= "SOC") +
#   annotate("text", x=15, y=3, label= "Chronic Care Clinic") +
#   annotate("text", x=15, y=2, label= "$13/DALY", color = "#2171B5") +
#   annotate("text", x=65, y=21, label= "CHW Screening") +
#   annotate("text", x=65, y=20, label= "$354/DALY", color = "#08306B") +
#   annotate("text", x=65, y=19, label= "$381/DALY", color = "#2171B5") +
#   annotate("text", x=65, y=18, label= "$305/DALY", color = "#6BAED6") +
#     coord_cartesian(ylim = c(0,30), xlim = c(0,70)) +
#   theme_minimal(base_size = 14) +
#   labs(title = "Cost-effectiveness of hypertension treatment policies (2024-2074)",
#        subtitle = "Alternative assumptions about screening costs",
#        y = "Annual incremental cost (millions $USD)",
#        x = "Annual DALYs averted (thousands)") +
#   theme(
#     plot.title = element_text(size = 16, face = "bold"),
#     axis.title.y = element_text(size = 14),
#     axis.title.x = element_text(size = 14),
#     legend.position = "bottom"
#   ) +
#   scale_color_manual(values = c("#6BAED6", "#2171B5", "#08306B"))
```



